---
title: "Downloads"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---
```{css, echo=FALSE}
h1,h2,h3,h4 {
  text-align: center;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Below are several download options. Make sure you read the corresponding model documentation

```{r, include = FALSE}
source("main.R", local = TRUE)
```

## Data

Download the whole data (1.9 GB)
This includes all RCPs: 2.6, 4.5, 6.0 and 8.5 
Moreover for each cell there is GDP (2005) and Population data (2005)
Agricultural production variables include production in tonnes (*prd*), 
produced value (*value*), produced calories (*cal_yld*) and value of cash crops (*cash_value*). Each of the variables (besides gdp and population) exists for all possible combinations of time, RCP and water supply conditions, where this is indicated in the variable name: 

* **variable_rcpXXX_2XXXsh_x** 

where rcpXXX is one of:

* rcp2p6
* rcp4p5
* rcp6p0
* rcp8p5

and 2XXXsh is one of:

* 2020sh for the period 2011-2040
* 2050sh for the period 2041-2070
* 2080sh for the period 2071-2100

lastly _x is one of:

* _r for rainfed conditions
* _i for irrigated conditions

For all current data there is no suffix indicating rcp and time. Check the section `Data` in the model documentation: 

```{r, echo=FALSE}
download_link(
  link = "https://drive.google.com/file/d/1fc8NFAsMsH3I2atjT1_TMvy8ARaccrUF/view?usp=sharing",
  button_label = "Model Documentation",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```

<br>

## Maps 

Click below to download one of the high resolution map presented on this site. For more information on the creation of the maps go to the corresponding RCP in the `Maps` section. (Under Construction)

Absolute Changes RCP 2.6
```{r, echo=FALSE}
download_link(
  link = "https://drive.google.com/file/d/1TE0Y-UhQZVh3w2TZ8CCV1Q_9mhAChLFt/view?usp=sharing",
  button_label = "Map RCP 2.6",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```

Absolute Changes RCP 6.0

```{r, echo=FALSE}
download_link(
  link = "https://drive.google.com/file/d/1BHdGl7oS4vJpVaWRrzo3qPPRhnFk5rl1/view?usp=sharing",
  button_label = "Map RCP 6.0",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```

Absolute Changes RCP 8.5

```{r, echo=FALSE}
download_link(
  link = "https://drive.google.com/file/d/1_x0YpVYGULnZvuDGa0eeifdFbn-9QUov/view?usp=sharing",
  button_label = "Map RCP 8.5",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```










