---
title: "Test RCP 2.6"

output: html_document
---
<style>
body {
text-align: justify}
</style>

```{css, echo=FALSE}
h1,h2,h3,h4 {
  text-align: center;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


RCP 2.6 is a scenario that assumes very aggressive reductions in greenhouse gas emissions, resulting in a relatively low level of warming and minimal sea level rise.

Below you can view the absolute and relative change maps. Check the [Map Description](map_description.html) for information about the creation of the map, especially the creation of the bins.

Note that Change relates to differences between the time period 2070-2100 to today. We express calories in People Fed Yearly (**PFY**)

<br>

```{r, include = F}

#source("main.R", local = TRUE)
source("leaflet.R", local = TRUE)
```

```{r, warning=FALSE}
map1 <- leaflet_function(absolute_tifs[1], "Absolute PFY Change")
map2 <- leaflet_function(relative_tifs[1], "Growth Rate")
print(map1)
print(map2)
```

```{r, results = 'asis'}
cat('<button onclick="toggleMaps()">Toggle Maps</button>')

cat('
<script>
function toggleMaps() {
  var map1 = document.getElementById("map1");
  var map2 = document.getElementById("map2");
  
  if (map1.style.display === "none") {
    map1.style.display = "block";
    map2.style.display = "none";
  } else {
    map1.style.display = "none";
    map2.style.display = "block";
  }
}
</script>
')

cat('
<style>
button {
  background-color: #4CAF50;
  color: white;
  padding: 8px 16px;
  border: none;
  cursor: pointer;
}

#map1 {
  display: block;
}

#map2 {
  display: none;
}
</style>
')


``` 
