---
title: "RCP2.6"

output: html_document
---
<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


RCP 2.6 is a scenario that assumes very aggressive reductions in greenhouse gas emissions, resulting in a relatively low level of warming and minimal sea level rise.

Below you can view the absolute and relative change maps. Check the [Map Description](map_description.html) for information about the creation of the map, especially the creation of the bins.

Below the maps you can download a high resolution pdf for each map.



```{r, include = F}

#source("main.R", local = TRUE)
source("leaflet.R", local = TRUE)
```

### Absolute Change under RCP 2.6
```{r, echo = F, warning = F, out.width = "100%"}
leaflet_function(absolute_tifs[1], "Absolute PFY Change")
```


However, cells that have a lot of agricultural production will exhibit large absolute changes even under small relative changes and vice versa. Therefore it is important to simultaneously take the growth rate into account. 

<br>

### Relative Change under RCP 2.6
```{r, echo = F, warning = F, out.width="100%"}
leaflet_function(relative_tifs[1], "Growth Rate")
```


