---
title: "RCP 6.0"

output: html_document
---

```{css, echo=FALSE}
h1,h2,h3,h4 {
  text-align: center;
}
```

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}

#source("main.R", local = TRUE)
source("leaflet.R", local = TRUE)
```

RCP 6.0 is a scenario that assumes moderate reductions in greenhouse gas emissions, resulting in a moderate level of warming and moderate sea level rise.

Below you can view the absolute and relative change maps. Check the [Map Description](map_description.html) for information about the creation of the map, especially the creation of the bins. 
Note that Change relates to differences between the time period 2070-2100 to today. We express calories in People Fed Yearly (**PFY**)

<br>

### Absolute Change under RCP 6.0
<br>
```{r, echo = F, warning = F, out.width = "100%"}
leaflet_function(absolute_tifs[2], "Absolute PFY Change")
```

However, cells that have a lot of agricultural production will exhibit large absolute changes even under small relative changes and vice versa. Therefore it is important to simultaneously take the growth rate into account.

<br>

### Relative Change under RCP 6.0
<br>
```{r, echo = F, warning = F, out.width="100%"}
leaflet_function(relative_tifs[2], "Growth Rate")