---
title: "RCP 8.5"
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}

#source("main.R", local = TRUE)
source("leaflet.R", local = TRUE)
```

RCP 8.5 is a scenario that assumes very little reduction in greenhouse gas emissions, resulting in a high level of warming and significant sea level rise.

Below you can view the absolute and relative change maps. Check the [Map Description](map_description.html) for information about the creation of the map, especially the creation of the bins. 
Below the maps you can download a high resolution pdf for each map.

<br>

### Absolute Change under RCP 8.5
```{r, echo = F, warning = F, out.width = "100%"}
leaflet_function(absolute_tifs[3], "Absolute PFY Change")
```

However, cells that have a lot of agricultural production will exhibit large absolute changes even under small relative changes and vice versa. Therefore it is important to simultaneously take the growth rate into account.


### Relative Change under RCP 8.5
```{r, echo = F, warning = F, out.width="100%"}
leaflet_function(relative_tifs[3], "Growth Rate")